---
title: "ABC13 Neighborhood Safety Tracker"
# author: "John Kelly"
date: "Updated 6/1/2022 by the ABC13 Data Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(tidycensus)
library(readxl)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(sp)
library(sf)
library(htmlwidgets)
library(htmltools)

# rmarkdown::render('Houston_Safety_Tracker_2.Rmd', output_file = 'docs/Houston_Safety_Tracker_2.html')
```
<link href="https://fonts.googleapis.com/css2?family=Roboto:wght@100;300;400;500;700;900&display=swap" rel="stylesheet">

```{css, echo=FALSE}

          
.title {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 45px;
    padding: 5px;
}

.date {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: center;
  font-size: 12px;
    padding: 5px;
}

select {
  margin: 0px;
  width: 180px;
  color: #00318b;
  padding: 5px 35px 5px 5px;
    font-family: roboto;
  font-size: 18px;
  font-weight: 900;
  border: 0px;
  height: 34px;
  -webkit-appearance: none;
  -moz-appearance: none;
  appearance: none;
  background: url(https://upload.wikimedia.org/wikipedia/commons/9/9d/Arrow-down.svg) 96% / 15% no-repeat #f2f2f2;
}

h1 {
  font-family: roboto;
  color: black;
  font-weight: bolder;
  text-align: left;
  font-size: 36px;
  margin-top: 0;
  margin-bottom: 0;
}

h2 {
  font-family: roboto;
  font-weight: 500;
  color: black;
  text-align: center;
  font-size: 18px;
  margin-top: 0;
  margin-bottom: 2;
}

bignumber {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 60px;
    line-height: 65px;
  height: 65px;
    margin-top: 0;
  margin-bottom: 0;
}

subhead {
  font-family: roboto;
  color: black;
  font-weight: 700;
  text-align: left;
  font-size: 20px;
    padding: 0px;
}

body {
  color: black;
  font-family: roboto;
  font-weight: 400;
  font-size: 18px;
}

popuptitle {
  color: #00318b;
  font-family: roboto;
  font-weight: 700;
  font-size: 15px;
  text-align: left;
}

popupchatter {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: left;
  font-size: 12px;
  margin-top: 0;
  margin-bottom: 2;
}

h8 {
  color: #00318b;
  font-family: roboto;
  font-weight: 900;
  font-size: 18px;
}

table {
  font-family: roboto;
  width: 100%;
}

tr {
  border-bottom: thin solid #99a0a5;
}
  
td {
  text-align: right;
  padding: 1px;
}

th {
  text-align: right;
  padding: 1px;
}

   * {
      box-sizing: border-box;
   }
   .card {
      color: white;
      float: left;
      width: calc(25% - 20px);
      padding: 10px;
      border-radius: 10px;
      margin: 10px;
      height: 100%;
   }
   .card p {
   font-family: roboto;
   text-align: center;
   font-size: 14px;
  margin-bottom: 0;
   }
   .cardContainer:after {
      content: "";
      display: table;
      clear: both;
   }
   @media screen and (max-width: 650px) {
      .card {
         width: 100%;
      }

   }
```

```{r beats, include=FALSE}
# source("process_houston_police_beats.R")
```


```{r crimedata, include=FALSE}
# source("process_houston_crime_data.R")
```

<h2>ABC13's data team is tracking crime and safety across Houston and in your neighborhood.<br>You can choose which crime to examine: <select onchange="window.location=this.value">
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Burglaries.html">Burglaries</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Assaults.html">Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_AutoThefts.html">Auto Thefts</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Burglaries.html">Burglaries</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_DrugCrimes.html">Drug Crimes</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker.html">Homicides</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Robberies.html">Robberies</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_SexualAssaults.html">Sexual Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Thefts.html">Thefts</option>
</select></h2>

<div class="cardContainer">
<div class="card" style="background-color:#99a0a5;">
<p>Burglaries<br>
<bignumber>`r prettyNum(burglaries_city$last12mos, big.mark=",")`<br></bignumber>
<p>Last 12 months<br>Through April 2022</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Burglaries<br>
<bignumber>`r prettyNum(round(burglaries_city$avg_prior3years,0), big.mark=",")`<br></bignumber><p>
Yearly average<br>2019 to 2021</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Burglary Rate<br>
<bignumber>`r burglaries_city$rate_last12`<br></bignumber><p>
Per 100,000 people<br>Last 12 months</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Burglary Rate<br>
<bignumber>`r burglaries_city$rate_prior3years`<br></bignumber><p>
Per 100,000 people<br>2019 to 2021</p>
</div>
</div>
<br>
Burglaries are <h8>`r ifelse(burglaries_city$inc_prior3yearavgtolast12>=0," up"," down")` `r ifelse(burglaries_city$inc_prior3yearavgtolast12>=0,burglaries_city$inc_prior3yearavgtolast12,substring(burglaries_city$inc_prior3yearavgtolast12,2))`%</h8> over the last 12 months compared to the average from 2019-2021.

The city averaged <h8>`r round(burglaries_city$last12mos/52,0)`</h8> burglaries a week since last May. In 2019, that number was <h8>`r round(burglaries_city$total19/52,0)`</h8> a week.

The risk is not the same neighborhood to neighborhood.

About <h8>`r round(pop_burglariesdown/2304580*100,0)`%</h8> of city residents live in neighborhoods where the burglary rate over the last 12 months is down or about the same as the three-year average. About <h8>`r round(pop_burglariesup/2304580*100,0)`%</h8> live in neighborhoods where the burglary rate is up more than 20%.

ABC13's data team looked at the Houston Police Department's data by neighborhood from 2019 through last month.

<subhead>A closer look at Houston burglaries neighborhood by neighborhood</subhead>

The map color-codes each neighborhood by the burglary rate over the last 12 months, through the end of April, which is the most recent comprehensive data released by the Houston Police Department.

The yellow areas are neighborhoods where the burglary rate is among the 25% highest rates in the city.

Click on any neighborhood on the map to see detailed figures, rates and trends. You can also search for a street name, place, landmark or zip code.

<br>
```{r cars, echo=FALSE,out.width='100%',out.height='600'}
# burglary MAP

# Set bins for numbers of crimes for burglaries map
burglarypal <- colorQuantile(c("#667f99",
                             "#00318b",
                             "#0058f6",
                             "#ffba00"), burglaries_beat$rate_prior3years, n = 4, na.color = NA)

# Create quick labels for burglaries map
burglarylabel <- paste(sep="",
ifelse(burglaries_beat$inc_prior3yearavgtolast12>=0,
       "<popuptitle>Burglaries are up ",
       "<popuptitle>Burglaries are down "),
ifelse(burglaries_beat$inc_prior3yearavgtolast12>=0,burglaries_beat$inc_prior3yearavgtolast12,substring(burglaries_beat$inc_prior3yearavgtolast12,2)),
				"%</popuptitle><br><popupchatter>the last 12 months vs. the 3-year average in the area including ",
burglaries_beat$placename,
".
<br>
<table>      
      <tr>
				<th></th>
				<th>Total</th>
				<th>Rate</th>
			</tr>
			<tr>
				<td>2019</td>
				<td>",
burglaries_beat$total19,
"</td>
				<td>",
burglaries_beat$rate19,
"</td>
			</tr>
			<tr>
				<td>2020</td>
				<td>",
burglaries_beat$total20,
"</td>
				<td>",
burglaries_beat$rate20,
"</td>
			</tr>
						<tr>
				<td>2021</td>
				<td>",
burglaries_beat$total21,
"</td>
				<td>",
burglaries_beat$rate21,
"</td>
			</tr>
						<tr>
				<td>Last 12 months</td>
				<td>",
burglaries_beat$last12mos,
"</td>
				<td>",
burglaries_beat$rate_last12,
"</td>
			</tr>
						<tr>
				<td>3-year Average</td>
				<td>",
burglaries_beat$avg_prior3years,
"</td>
				<td>",
burglaries_beat$rate_prior3years,
"</td>
			</tr>
</table>")

# Creating police beats map for types of crimes
houston_burglary_map <- leaflet(burglaries_beat, options = leafletOptions(zoomControl = FALSE)) %>%
  htmlwidgets::onRender("function(el, x) {
L.control.zoom({ position: 'topright' }).addTo(this)
}") %>%
  setView(-95.5, 29.75, zoom = 11) %>% 
  addProviderTiles(provider = "CartoDB.Positron") %>%
  addPolygons(color = "white", 
              popup = burglarylabel, 
              popupOptions = popupOptions(maxWidth ="200", 
                                          minWidth ="200"),
              weight = 2, 
              smoothFactor = 0.5,
              opacity = 0.6, 
              fillOpacity = 0.5,
              fillColor = ~burglarypal(rate_prior3years)) %>% 
    addSearchOSM(options = searchOptions(autoCollapse=FALSE, minLength = 3,zoom=13, position="topleft")) %>%
  addLegend(opacity = 0.6,
            values = burglaries_beat$rate_prior3years, 
            colors = c("#667f99",
                       "#00318b",
                       "#0058f6",
                       "#ffba00"),
            labels=c("Lowest Rate", 
                     "Lower Rate", 
                     "Higher Rate", 
                     "Highest Rate"),
            position = "bottomleft", 
            title = "<popuptitle>Burglaries per 100,000 people")  

houston_burglary_map
```
<br>
About <h8>`r round(pop_burglariesmonthly/2304580*100,0)`%</h8> of Houston residents now live in neighborhoods where there was at least one burglary every month over the last year. Here's a look at burglaries citywide every month since 2019.
<br>
<!-- <subhead>Burglaries month by month, 2019 through last month</subhead> -->

<iframe title="Burglaries month by month, 2019 through last month" aria-label="Column Chart" id="datawrapper-chart-gG4we" src="https://datawrapper.dwcdn.net/gG4we/1/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="400" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
  <br>
<br>
<!-- <subhead>Risk of being burglarized in Houston vs. other crimes in Houston</subhead> -->

<iframe title="Risk of property crimes across Houston" aria-label="Dot Plot" id="datawrapper-chart-HVqY5" src="https://datawrapper.dwcdn.net/HVqY5/5/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="178" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
<br>
<br>
<!-- Will be adding additional contextual charting around this crime category -->