---
title: "ABC13 Neighborhood Safety Tracker"
# author: "John Kelly"
date: "Updated 4/6/2022 by the ABC13 Data Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(tidycensus)
library(readxl)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(sp)
library(sf)
library(htmlwidgets)
library(htmltools)

# rmarkdown::render('Houston_Safety_Tracker_2.Rmd', output_file = 'docs/Houston_Safety_Tracker_2.html')
```
<link href="https://fonts.googleapis.com/css2?family=Roboto:wght@100;300;400;500;700;900&display=swap" rel="stylesheet">

```{css, echo=FALSE}

          
.title {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 45px;
    padding: 5px;
}

.date {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: center;
  font-size: 12px;
    padding: 5px;
}

select {
  margin: 0px;
  width: 175px;
  color: #00318b;
  padding: 5px 35px 5px 5px;
    font-family: roboto;
  font-size: 18px;
  font-weight: 900;
  border: 0px;
  height: 34px;
  -webkit-appearance: none;
  -moz-appearance: none;
  appearance: none;
  background: url(https://upload.wikimedia.org/wikipedia/commons/9/9d/Arrow-down.svg) 96% / 15% no-repeat #f2f2f2;
}

h1 {
  font-family: roboto;
  color: black;
  font-weight: bolder;
  text-align: left;
  font-size: 36px;
  margin-top: 0;
  margin-bottom: 0;
}

h2 {
  font-family: roboto;
  font-weight: 500;
  color: black;
  text-align: center;
  font-size: 18px;
  margin-top: 0;
  margin-bottom: 2;
}

bignumber {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 60px;
    line-height: 65px;
  height: 65px;
    margin-top: 0;
  margin-bottom: 0;
}

popupchatter {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: left;
  font-size: 12px;
  margin-top: 0;
  margin-bottom: 2;
}

chartbignumber {
  font-family: roboto;
  color: #00318b;
  font-weight: bolder;
  text-align: right;
  font-size: 36px;
    margin-top: 0;
  margin-bottom: 0;
}

subhead {
  font-family: roboto;
  color: black;
  font-weight: 700;
  text-align: left;
  font-size: 20px;
    padding: 0px;
}

body {
  color: black;
  font-family: roboto;
  font-weight: 400;
  font-size: 16px;
}

popuptitle {
  font-family: roboto;
  color: #00318b;
  font-weight: bolder;
  text-align: left;
  font-size: 20px;
    margin-top: 0;
  margin-bottom: 0;
}

h8 {
  color: #00318b;
  font-family: roboto;
  font-weight: 900;
  font-size: 16px;
}

table {
  font-family: roboto;
  border-collapse: collapse;
  width: 100%;
}

tr {
  border-bottom: thin solid #99a0a5;
}
  
td {
  text-align: right;
  padding: 6px;
}

th {
  text-align: right;
  padding: 6px;
}

   * {
      box-sizing: border-box;
   }
   .card {
      color: white;
      float: left;
      width: calc(25% - 20px);
      padding: 10px;
      border-radius: 10px;
      margin: 10px;
      height: 100%;
   }
   .card p {
   font-family: roboto;
   text-align: center;
   font-size: 12px;
  margin-bottom: 0;
   }
   .cardContainer:after {
      content: "";
      display: table;
      clear: both;
   }
   @media screen and (max-width: 650px) {
      .card {
         width: 100%;
      }

   }
```

```{r beats, include=FALSE}
# source("process_houston_police_beats.R")
```


```{r crimedata, include=FALSE}
# source("process_houston_crime_data.R")
```

<h2>ABC13's data team is tracking crime and safety across Houston and in your neighborhood.<br>You can choose which crime to examine: <select onchange="window.location=this.value">
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_DrugCrimes.html">Drug Crimes</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker.html">Homicides</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_SexualAssaults.html">Sexual Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_AutoThefts.html">Auto Thefts</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Assaults.html">Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Thefts.html">Thefts</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Burglaries.html">Burglaries</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Robberies.html">Robberies</option>
</select></h2>

<div class="cardContainer">
<div class="card" style="background-color:#99a0a5;">
<p>So far this year<br>
<bignumber>`r prettyNum(drugs_city$total22, big.mark=",")`<br></bignumber><p>
people have been druged.</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Over the last 12 momths,<br>
<bignumber>`r prettyNum(drugs_city$last12mos, big.mark=",")`<br></bignumber>
<p>people have been killed.</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>The yearly average is<br>
<bignumber>`r prettyNum(round(drugs_city$avg_prior3years,0), big.mark=",")`<br></bignumber><p>
from 2019 to 2021.</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>The drug crime rate is <br>
<bignumber>`r round(drugs_city$rate_last12,0)`<br></bignumber><p>
per 100K people the last year.</p>
</div>
</div>
<br>
About three years ago, the drug crime rate in Houston was <h8>`r round(drugs_city$rate19,0)`</h8> per 100,000 residents.

The average drug crime rate for the three-year period from 2019 to 2022 was <h8>`r round(drugs_city$rate_prior3years,0)`</h8> and last year it was <h8>`r round(drugs_city$rate21,0)`</h8>.

The situation, of course, is not the same neighborhood to neighborhood.

About <h8>`r round(pop_drugsdown/2304580*100,0)`%</h8> of city residents live in neighborhoods where the drug crime rate over the last 12 months is down or about the same as the three-year average. 

But, about <h8>`r round(pop_drugsup/2304580*100,0)`%</h8> of Houston residents live in neighborhoods where the drug crime rate is up more than 20% in the last 12 months when compared to the three-year average from 2019 to 2021.

And, <h8>`r round(pop_drugsmonthly/2304580*100,0)`%</h8> of us now live in neighborhoods where there was at least one drug every month over the last year.

Across the city the last 12 months, there were about <h8>`r round(drugs_city$last12mos/52,0)`</h8> drug crimes every week. In 2019, that number was <h8>`r round(drugs_city$total19/52,0)`</h8> per week

<subhead>Houston drug crimes neighborhood by neighborhood</subhead>

ABC13 looked at the Houston Police Department's data, beat by beat across the city and is providing this look at the drug trends by neighborhood for each of the last four years in the map below. The color-coding of the map is based on the drug crime rate over 2019, 2020 and 2021 combined, according to ABC13's analysis of data the city police department publishes monthly.

```{r cars, echo=FALSE,out.width='100%',out.height='600'}
# drug MAP

# Set bins for numbers of crimes for drugs map
drugpal <- colorQuantile(c("#667f99",
                             "#00318b",
                             "#0058f6",
                             "#ffba00"), drugs_beat$rate_prior3years, n = 4, na.color = NA)

# Create quick labels for drugs map
druglabel <- paste(sep="",
"<table>
<popuptitle>Houston P.D. Beat #",
drugs_beat$beat,
"</popuptitle><br><popupchatter>Area neighborhoods and landmarks include ",
drugs_beat$placename,
". Estimated Population: ",
prettyNum(drugs_beat$population, big.mark=','),
"</popupchatter><br>
      <tr>
				<th></th>
				<th>Total</th>
				<th>Rate</th>
				<th>Trend</th>
			</tr>
			<tr>
				<td>2019</td>
				<td>",
drugs_beat$total19,
"</td>
				<td>",
drugs_beat$rate19,
"</td>
				<!-- Insert cell to cross/span 
				multi rows -->
				<td rowspan='5'>",
ifelse(drugs_beat$inc_prior3yearavgtolast12>=0,"Last 12<br>months up","Last 12<br>months down"),
"<br><chartbignumber>",
ifelse(drugs_beat$inc_prior3yearavgtolast12>=0,drugs_beat$inc_prior3yearavgtolast12,substring(drugs_beat$inc_prior3yearavgtolast12,2)),
				"%</chartbignumber><br>vs. 3-year<br>average</td>
			</tr>
			<tr>
				<td>2020</td>
				<td>",
drugs_beat$total20,
"</td>
				<td>",
drugs_beat$rate20,
"</td>
			</tr>
						<tr>
				<td>2021</td>
				<td>",
drugs_beat$total21,
"</td>
				<td>",
drugs_beat$rate21,
"</td>
			</tr>
						<tr>
				<td>Last 12 months</td>
				<td>",
drugs_beat$last12mos,
"</td>
				<td>",
drugs_beat$rate_last12,
"</td>
			</tr>
						<tr>
				<td>3-year Average</td>
				<td>",
drugs_beat$avg_prior3years,
"</td>
				<td>",
drugs_beat$rate_prior3years,
"</td>
			</tr>
</table>")

# Creating police beats map for types of crimes
houston_drug_map <- leaflet(drugs_beat, options = leafletOptions(zoomControl = FALSE)) %>%
  htmlwidgets::onRender("function(el, x) {
L.control.zoom({ position: 'topright' }).addTo(this)
}") %>%
  setView(-95.4, 29.75, zoom = 12) %>% 
  addProviderTiles(provider = "Stamen.TonerLite") %>%
  addPolygons(color = "white", 
              popup = druglabel, 
              weight = 0.5, 
              smoothFactor = 0.5,
              opacity = 0.6, 
              fillOpacity = 0.5,
              fillColor = ~drugpal(rate_prior3years)) %>% 
  addLegend(opacity = 0.6,
            values = drugs_beat$rate_prior3years, 
            colors = c("#667f99",
                       "#00318b",
                       "#0058f6",
                       "#ffba00"),
            labels=c("Lowest Rate", 
                     "Lower Rate", 
                     "Higher Rate", 
                     "Highest Rate"),
            position = "bottomleft", 
            title = "Drug Crimes<br>Per 100K people<br>") 

houston_drug_map
```

However, in the vast majority of neighborhoods in the city, the rate is much lower. In 17 of 118 of the Houston Police Department's, the drug crime rate was zero last year. Filler, filler, filler.
<br>
<br>
<!-- <subhead>Drug crimes month by month, 2019 through last month</subhead> -->

<iframe title="Drug crimes month by month, 2019 through last month" aria-label="Column Chart" id="datawrapper-chart-8Hhfx" src="https://datawrapper.dwcdn.net/8Hhfx/2/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="400" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
  <br>
<br>
<!-- <subhead>Risk of being murdered in Houston vs. other causes of death in Texas</subhead> -->

<iframe title="" aria-label="Dot Plot" id="datawrapper-chart-9SHHa" src="https://datawrapper.dwcdn.net/9SHHa/5/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="146" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
<br>
<br>
<!-- <subhead>What kinds of places do murders happen in Houston</subhead> -->

<iframe title="What kinds of places do murders happen in Houston"  aria-label="Table" id="datawrapper-chart-xI2y0" src="https://datawrapper.dwcdn.net/xI2y0/10/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="1239" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
<br>
<br>
<!-- <subhead>What time of day do murders happen?</subhead> -->

<iframe title="What hour of day do murders happen" aria-label="Column Chart" id="datawrapper-chart-coxAA" src="https://datawrapper.dwcdn.net/coxAA/7/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="400" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
