---
title: "ABC13 Neighborhood Safety Tracker"
# author: "John Kelly"
date: "Updated 4/26/2022 by the ABC13 Data Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(tidycensus)
library(readxl)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(sp)
library(sf)
library(htmlwidgets)
library(htmltools)

# rmarkdown::render('Houston_Safety_Tracker_2.Rmd', output_file = 'docs/Houston_Safety_Tracker_2.html')
```
<link href="https://fonts.googleapis.com/css2?family=Roboto:wght@100;300;400;500;700;900&display=swap" rel="stylesheet">

```{css, echo=FALSE}

          
.title {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 45px;
    padding: 5px;
}

.date {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: center;
  font-size: 12px;
    padding: 5px;
}

select {
  margin: 0px;
  width: 175px;
  color: #00318b;
  padding: 5px 35px 5px 5px;
    font-family: roboto;
  font-size: 18px;
  font-weight: 900;
  border: 0px;
  height: 34px;
  -webkit-appearance: none;
  -moz-appearance: none;
  appearance: none;
  background: url(https://upload.wikimedia.org/wikipedia/commons/9/9d/Arrow-down.svg) 96% / 15% no-repeat #f2f2f2;
}

h1 {
  font-family: roboto;
  color: black;
  font-weight: bolder;
  text-align: left;
  font-size: 36px;
  margin-top: 0;
  margin-bottom: 0;
}

h2 {
  font-family: roboto;
  font-weight: 500;
  color: black;
  text-align: center;
  font-size: 18px;
  margin-top: 0;
  margin-bottom: 2;
}

bignumber {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 60px;
    line-height: 65px;
  height: 65px;
    margin-top: 0;
  margin-bottom: 0;
}

popupchatter {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: left;
  font-size: 12px;
  margin-top: 0;
  margin-bottom: 2;
}

chartbignumber {
  font-family: roboto;
  color: #00318b;
  font-weight: bolder;
  text-align: right;
  font-size: 36px;
    margin-top: 0;
  margin-bottom: 0;
}

subhead {
  font-family: roboto;
  color: black;
  font-weight: 700;
  text-align: left;
  font-size: 20px;
    padding: 0px;
}

body {
  color: black;
  font-family: roboto;
  font-weight: 400;
  font-size: 16px;
}

popuptitle {
  font-family: roboto;
  color: #00318b;
  font-weight: bolder;
  text-align: left;
  font-size: 20px;
    margin-top: 0;
  margin-bottom: 0;
}

h8 {
  color: #00318b;
  font-family: roboto;
  font-weight: 900;
  font-size: 16px;
}

table {
  font-family: roboto;
  border-collapse: collapse;
  width: 100%;
}

tr {
  border-bottom: thin solid #99a0a5;
}
  
td {
  text-align: right;
  padding: 6px;
}

th {
  text-align: right;
  padding: 6px;
}

   * {
      box-sizing: border-box;
   }
   .card {
      color: white;
      float: left;
      width: calc(25% - 20px);
      padding: 10px;
      border-radius: 10px;
      margin: 10px;
      height: 100%;
   }
   .card p {
   font-family: roboto;
   text-align: center;
   font-size: 14px;
  margin-bottom: 0;
   }
   .cardContainer:after {
      content: "";
      display: table;
      clear: both;
   }
   @media screen and (max-width: 650px) {
      .card {
         width: 100%;
      }

   }
```

```{r beats, include=FALSE}
# source("process_houston_police_beats.R")
```


```{r crimedata, include=FALSE}
# source("process_houston_crime_data.R")
```

<h2>ABC13 is tracking crime and safety across Houston and in your neighborhood.<br>You can choose which crime to examine: <select onchange="window.location=this.value">
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Robberies.html">Robberies</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker.html">Homicides</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_SexualAssaults.html">Sexual Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_AutoThefts.html">Auto Thefts</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Assaults.html">Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Thefts.html">Thefts</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Burglaries.html">Burglaries</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_DrugCrimes.html">Drug Crimes</option>
</select></h2>

<div class="cardContainer">
<div class="card" style="background-color:#99a0a5;">
<p>Robberies<br>
<bignumber>`r prettyNum(robberies_city$last12mos, big.mark=",")`<br></bignumber>
<p>Last 12 months<br>Through April 2022</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Robberies<br>
<bignumber>`r prettyNum(round(robberies_city$avg_prior3years,0), big.mark=",")`<br></bignumber><p>
Yearly average<br>2019 to 2021</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Robbery Rate<br>
<bignumber>`r round(robberies_city$rate_last12,0)`<br></bignumber><p>
Per 100,000 people<br>Last 12 months</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Robbery Rate<br>
<bignumber>`r round(robberies_city$rate_prior3years,0)`<br></bignumber><p>
Per 100,000 people<br>2019 to 2021</p>
</div>
</div>
<br>
Over the last 12 months, there were about <h8>`r round(robberies_city$last12mos/52,0)`</h8> robberies every week in Houston. In 2019, that number was <h8>`r round(robberies_city$total19/52,0)`</h8> per week.

The average robbery rate for the three-year period from 2019 to 2022 was <h8>`r round(robberies_city$rate_prior3years,0)`</h8> per 100,000 residents. Last year, the rate was <h8>`r round(robberies_city$rate21,0)`</h8>.

The risk, of course, is not the same neighborhood to neighborhood.

About <h8>`r round(pop_robberiesdown/2304580*100,0)`%</h8> of city residents live in neighborhoods where the robbery rate over the last 12 months is down or about the same as the three-year average. About <h8>`r round(pop_robberiesup/2304580*100,0)`%</h8> live in neighborhoods where the robbery rate is up more than 20%.

<subhead>A closer look at Houston robberies neighborhood by neighborhood</subhead>

So, ABC13's data team looked at the Houston Police Department's data, beat by beat across the city to provide this look at trends by neighborhood from 2019 through last month.

The map color-codes each neighborhood by the robbery rate over the last 12 months, through the end of April, which is the most recent comprehensive data released by the Houston Police Department.

The yellow areas are neighborhoods where the robbery rate is among the 25% highest rates in the city. You can click on any neighborhood to see detailed figures, rates and trends.

ABC13 will be updating this data every month.
<br>
<br>
```{r cars, echo=FALSE,out.width='100%',out.height='600'}
# robbery MAP

# Set bins for numbers of crimes for robberies map
robberypal <- colorQuantile(c("#667f99",
                             "#00318b",
                             "#0058f6",
                             "#ffba00"), robberies_beat$rate_prior3years, n = 4, na.color = NA)

# Create quick labels for robberies map
robberylabel <- paste(sep="",
"<table>
<popuptitle>Houston P.D. Beat #",
robberies_beat$beat,
"</popuptitle><br><popupchatter>Area neighborhoods and landmarks include ",
robberies_beat$placename,
". Estimated Population: ",
prettyNum(robberies_beat$population, big.mark=','),
"</popupchatter><br>
      <tr>
				<th></th>
				<th>Total</th>
				<th>Rate</th>
				<th>Trend</th>
			</tr>
			<tr>
				<td>2019</td>
				<td>",
robberies_beat$total19,
"</td>
				<td>",
robberies_beat$rate19,
"</td>
				<!-- Insert cell to cross/span 
				multi rows -->
				<td rowspan='5'>",
ifelse(robberies_beat$inc_prior3yearavgtolast12>=0,
       "Last 12<br>months up<br><chartbignumber><span style='color:#00318b'>&#8593;</span>",
       "Last 12<br>months down <br><chartbignumber><span style='color:#00318b'>&#8595;</span>"),
ifelse(robberies_beat$inc_prior3yearavgtolast12>=0,robberies_beat$inc_prior3yearavgtolast12,substring(robberies_beat$inc_prior3yearavgtolast12,2)),
				"%</chartbignumber><br>vs. 3-year<br>average</td>
			</tr>
			<tr>
				<td>2020</td>
				<td>",
robberies_beat$total20,
"</td>
				<td>",
robberies_beat$rate20,
"</td>
			</tr>
						<tr>
				<td>2021</td>
				<td>",
robberies_beat$total21,
"</td>
				<td>",
robberies_beat$rate21,
"</td>
			</tr>
						<tr>
				<td>Last 12 months</td>
				<td>",
robberies_beat$last12mos,
"</td>
				<td>",
robberies_beat$rate_last12,
"</td>
			</tr>
						<tr>
				<td>3-year Average</td>
				<td>",
robberies_beat$avg_prior3years,
"</td>
				<td>",
robberies_beat$rate_prior3years,
"</td>
			</tr>
</table>")

# Creating police beats map for types of crimes
houston_robbery_map <- leaflet(robberies_beat, options = leafletOptions(zoomControl = FALSE)) %>%
  htmlwidgets::onRender("function(el, x) {
L.control.zoom({ position: 'topright' }).addTo(this)
}") %>%
  setView(-95.5, 29.75, zoom = 11) %>% 
  addProviderTiles(provider = "Stamen.TonerLite") %>%
  addPolygons(color = "white", 
              popup = robberylabel, 
              weight = 1, 
              smoothFactor = 0.5,
              opacity = 0.6, 
              fillOpacity = 0.5,
              fillColor = ~robberypal(rate_prior3years)) %>% 
  addLegend(opacity = 0.6,
            values = robberies_beat$rate_prior3years, 
            colors = c("#667f99",
                       "#00318b",
                       "#0058f6",
                       "#ffba00"),
            labels=c("Lowest Rate", 
                     "Lower Rate", 
                     "Higher Rate", 
                     "Highest Rate"),
            position = "topleft", 
            title = "<popuptitle>Houston Neighborhood Robberies Map</popuptitle><br><popupchatter>Explore robberies per 100,000 people in your neighborhood</popupchatter><br>") 

houston_robbery_map
```

<br>
About <h8>`r round(pop_burglariesmonthly/2304580*100,0)`%</h8> of Houston residents now live in neighborhoods where there was at least one robbery every month over the last year. Here's a look at robberies citywide every month since 2019.
<br>
<br>
<!-- <subhead>Robberies month by month, 2019 through last month</subhead> -->

<iframe title="Robberies month by month, 2019 through last month" aria-label="Column Chart" id="datawrapper-chart-6BRuf" src="https://datawrapper.dwcdn.net/6BRuf/2/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="400" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
  <br>
<br>
<!-- <subhead>Risk of being murdered in Houston vs. other causes of death in Texas</subhead> -->

<iframe title="Risk of property crimes across Houston" aria-label="Dot Plot" id="datawrapper-chart-HVqY5" src="https://datawrapper.dwcdn.net/HVqY5/2/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="178" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
<br>
