---
title: "ABC13 Neighborhood Safety Tracker"
# author: "John Kelly"
date: "Updated 4/26/2022 by the ABC13 Data Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(tidycensus)
library(readxl)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(sp)
library(sf)
library(htmlwidgets)
library(htmltools)

# rmarkdown::render('Houston_Safety_Tracker_2.Rmd', output_file = 'docs/Houston_Safety_Tracker_2.html')
```
<link href="https://fonts.googleapis.com/css2?family=Roboto:wght@100;300;400;500;700;900&display=swap" rel="stylesheet">

```{css, echo=FALSE}

          
.title {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 45px;
    padding: 5px;
}

.date {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: center;
  font-size: 12px;
    padding: 5px;
}

select {
  margin: 0px;
  width: 150px;
  color: #00318b;
  padding: 5px 35px 5px 5px;
    font-family: roboto;
  font-size: 18px;
  font-weight: 900;
  border: 0px;
  height: 34px;
  -webkit-appearance: none;
  -moz-appearance: none;
  appearance: none;
  background: url(https://upload.wikimedia.org/wikipedia/commons/9/9d/Arrow-down.svg) 96% / 15% no-repeat #f2f2f2;
}

h1 {
  font-family: roboto;
  color: black;
  font-weight: bolder;
  text-align: left;
  font-size: 36px;
  margin-top: 0;
  margin-bottom: 0;
}

h2 {
  font-family: roboto;
  font-weight: 500;
  color: black;
  text-align: center;
  font-size: 18px;
  margin-top: 0;
  margin-bottom: 2;
}

bignumber {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 60px;
    line-height: 65px;
  height: 65px;
    margin-top: 0;
  margin-bottom: 0;
}

popupchatter {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: left;
  font-size: 12px;
  margin-top: 0;
  margin-bottom: 2;
}

chartbignumber {
  font-family: roboto;
  color: #00318b;
  font-weight: bolder;
  text-align: right;
  font-size: 36px;
    margin-top: 0;
  margin-bottom: 0;
}

subhead {
  font-family: roboto;
  color: black;
  font-weight: 700;
  text-align: left;
  font-size: 20px;
    padding: 0px;
}

body {
  color: black;
  font-family: roboto;
  font-weight: 400;
  font-size: 16px;
}

popuptitle {
  font-family: roboto;
  color: #00318b;
  font-weight: bolder;
  text-align: left;
  font-size: 20px;
    margin-top: 0;
  margin-bottom: 0;
}

h8 {
  color: #00318b;
  font-family: roboto;
  font-weight: 900;
  font-size: 16px;
}

table {
  font-family: roboto;
  border-collapse: collapse;
  width: 100%;
}

tr {
  border-bottom: thin solid #99a0a5;
}
  
td {
  text-align: right;
  padding: 6px;
}

th {
  text-align: right;
  padding: 6px;
}

   * {
      box-sizing: border-box;
   }
   .card {
      color: white;
      float: left;
      width: calc(25% - 20px);
      padding: 10px;
      border-radius: 10px;
      margin: 10px;
      height: 100%;
   }
   .card p {
   font-family: roboto;
   text-align: center;
   font-size: 14px;
  margin-bottom: 0;
   }
   .cardContainer:after {
      content: "";
      display: table;
      clear: both;
   }
   @media screen and (max-width: 650px) {
      .card {
         width: 100%;
      }

   }
```

```{r beats, include=FALSE}
# source("process_houston_police_beats.R")
```


```{r crimedata, include=FALSE}
# source("process_houston_crime_data.R")
```

<h2>ABC13's data team is tracking crime and safety across Houston and in your neighborhood.<br>You can choose which crime to examine: <select onchange="window.location=this.value">
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Thefts.html">Thefts</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker.html">Homicides</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_SexualAssaults.html">Sexual Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_AutoThefts.html">Auto Thefts</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Assaults.html">Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Burglaries.html">Burglaries</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Robberies.html">Robberies</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_DrugCrimes.html">Drug Crimes</option>
</select></h2>

<div class="cardContainer">
<div class="card" style="background-color:#99a0a5;">
<p>Thefts<br>
<bignumber>`r prettyNum(thefts_city$last12mos, big.mark=",")`<br></bignumber>
<p>Last 12 months<br>Through April 2022</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Thefts<br>
<bignumber>`r prettyNum(round(thefts_city$avg_prior3years,0), big.mark=",")`<br></bignumber><p>
Yearly average<br>2019 to 2021</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Theft Rate<br>
<bignumber>`r prettyNum(round(thefts_city$rate_last12,0), big.mark=",")`<br></bignumber><p>
Per 100,000 people<br>Last 12 months</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Theft Rate<br>
<bignumber>`r prettyNum(round(thefts_city$rate_prior3years,0),big.mark=",")`<br></bignumber><p>
Per 100,000 people<br>2019 to 2021</p>
</div>
</div>
<br>
Across Houston over the last 12 months, there were about <h8>`r prettyNum(round(thefts_city$last12mos/52,0), big.mark=",")`</h8> thefts every week. In 2019, <h8>`r prettyNum(round(thefts_city$total19/52,0), big.mark=",")`</h8> thefts happened per week.

About three years ago, the theft rate in Houston was <h8>`r prettyNum(round(thefts_city$rate19,0),big.mark=",")`</h8> per 100,000 residents. However, during the pandemic years, the risk of being a victim of theft has been falling slightly.

The risk, of course, is not the same neighborhood to neighborhood.

About <h8>`r round(pop_theftsdown/2304580*100,0)`%</h8> of Houton residents live in neighborhoods where the theft rate is down or the same. About <h8>`r round(pop_theftsup/2304580*100,0)`%</h8> live in neighborhoods where the theft rate is up more than 20% in the last 12 months compared to the three-year average.  

<subhead>Houston thefts neighborhood by neighborhood</subhead>

ABC13's data team looked at the Houston Police Department's data, beat by beat across the city to provide this look at trends by neighborhood from 2019 through last month.

The map color-codes each neighborhood by the theft rate over the last 12 months, through the end of April, which is the most recent comprehensive data released by the Houston Police Department.

The yellow areas are neighborhoods where the theft rate is among the 25% highest rates in the city. You can click on any neighborhood to see detailed figures, rates and trends.

ABC13 will be updating this data every month.
<br>

```{r cars, echo=FALSE,out.width='100%',out.height='600'}
# theft MAP

# Set bins for numbers of crimes for thefts map
theftpal <- colorQuantile(c("#667f99",
                             "#00318b",
                             "#0058f6",
                             "#ffba00"), thefts_beat$rate_prior3years, n = 4, na.color = NA)

# Create quick labels for thefts map
theftlabel <- paste(sep="",
"<table>
<popuptitle>Houston P.D. Beat #",
thefts_beat$beat,
"</popuptitle><br><popupchatter>Area neighborhoods and landmarks include ",
thefts_beat$placename,
". Estimated Population: ",
prettyNum(thefts_beat$population, big.mark=','),
"</popupchatter><br>
      <tr>
				<th></th>
				<th>Total</th>
				<th>Rate</th>
				<th>Trend</th>
			</tr>
			<tr>
				<td>2019</td>
				<td>",
thefts_beat$total19,
"</td>
				<td>",
thefts_beat$rate19,
"</td>
				<!-- Insert cell to cross/span 
				multi rows -->
				<td rowspan='5'>",
ifelse(thefts_beat$inc_prior3yearavgtolast12>=0,
       "Last 12<br>months up<br><chartbignumber><span style='color:#00318b'>&#8593;</span>",
       "Last 12<br>months down <br><chartbignumber><span style='color:#00318b'>&#8595;</span>"),
ifelse(thefts_beat$inc_prior3yearavgtolast12>=0,thefts_beat$inc_prior3yearavgtolast12,substring(thefts_beat$inc_prior3yearavgtolast12,2)),
				"%</chartbignumber><br>vs. 3-year<br>average</td>
			</tr>
			<tr>
				<td>2020</td>
				<td>",
thefts_beat$total20,
"</td>
				<td>",
thefts_beat$rate20,
"</td>
			</tr>
						<tr>
				<td>2021</td>
				<td>",
thefts_beat$total21,
"</td>
				<td>",
thefts_beat$rate21,
"</td>
			</tr>
						<tr>
				<td>Last 12 months</td>
				<td>",
thefts_beat$last12mos,
"</td>
				<td>",
thefts_beat$rate_last12,
"</td>
			</tr>
						<tr>
				<td>3-year Average</td>
				<td>",
thefts_beat$avg_prior3years,
"</td>
				<td>",
thefts_beat$rate_prior3years,
"</td>
			</tr>
</table>")

# Creating police beats map for types of crimes
houston_theft_map <- leaflet(thefts_beat, options = leafletOptions(zoomControl = FALSE)) %>%
  htmlwidgets::onRender("function(el, x) {
L.control.zoom({ position: 'topright' }).addTo(this)
}") %>%
  setView(-95.5, 29.75, zoom = 11) %>% 
  addProviderTiles(provider = "Stamen.TonerLite") %>%
  addPolygons(color = "white", 
              popup = theftlabel, 
              weight = 1, 
              smoothFactor = 0.5,
              opacity = 0.6, 
              fillOpacity = 0.5,
              fillColor = ~theftpal(rate_prior3years)) %>% 
  addLegend(opacity = 0.6,
            values = thefts_beat$rate_prior3years, 
            colors = c("#667f99",
                       "#00318b",
                       "#0058f6",
                       "#ffba00"),
            labels=c("Lowest Rate", 
                     "Lower Rate", 
                     "Higher Rate", 
                     "Highest Rate"),
            position = "topleft", 
            title = "<popuptitle>Houston Neighborhood Thefts Map</popuptitle><br><popupchatter>Explore thefts per 100,000 people in your neighborhood</popupchatter><br>")  

houston_theft_map
```

However, in the vast majority of neighborhoods in the city, the rate is much lower. In 17 of 118 of the Houston Police Department's, the theft rate was zero last year. Filler, filler, filler.
<br>
<br>
<!-- <subhead>Thefts month by month, 2019 through last month</subhead> -->

<iframe title="Thefts month by month, 2019 through last month" aria-label="Column Chart" id="datawrapper-chart-J86iw" src="https://datawrapper.dwcdn.net/J86iw/2/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="400" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
  <br>
<br>
<!-- <subhead>Risk of theft compared to other property crimes coming soon to this space> -->

<iframe title="Risk of property crimes across Houston" aria-label="Dot Plot" id="datawrapper-chart-HVqY5" src="https://datawrapper.dwcdn.net/HVqY5/2/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="178" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
<br>
<br>
<!-- more potential context charts below -->
