---
title: "ABC13 Neighborhood Safety Tracker"
# author: "John Kelly"
date: "Updated 4/6/2022 by the ABC13 Data Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(tidycensus)
library(readxl)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(sp)
library(sf)
library(htmlwidgets)
library(htmltools)

# rmarkdown::render('Houston_Safety_Tracker_2.Rmd', output_file = 'docs/Houston_Safety_Tracker_2.html')
```
<link href="https://fonts.googleapis.com/css2?family=Roboto:wght@100;300;400;500;700;900&display=swap" rel="stylesheet">

```{css, echo=FALSE}

          
.title {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 45px;
    padding: 5px;
}

.date {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: center;
  font-size: 12px;
    padding: 5px;
}

select {
  margin: 0px;
  width: 175px;
  color: #00318b;
  padding: 5px 35px 5px 5px;
    font-family: roboto;
  font-size: 18px;
  font-weight: 900;
  border: 0px;
  height: 34px;
  -webkit-appearance: none;
  -moz-appearance: none;
  appearance: none;
  background: url(https://upload.wikimedia.org/wikipedia/commons/9/9d/Arrow-down.svg) 96% / 15% no-repeat #f2f2f2;
}

h1 {
  font-family: roboto;
  color: black;
  font-weight: bolder;
  text-align: left;
  font-size: 36px;
  margin-top: 0;
  margin-bottom: 0;
}

h2 {
  font-family: roboto;
  font-weight: 500;
  color: black;
  text-align: center;
  font-size: 18px;
  margin-top: 0;
  margin-bottom: 2;
}

bignumber {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 60px;
    line-height: 65px;
  height: 65px;
    margin-top: 0;
  margin-bottom: 0;
}

popupchatter {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: left;
  font-size: 12px;
  margin-top: 0;
  margin-bottom: 2;
}

chartbignumber {
  font-family: roboto;
  color: #00318b;
  font-weight: bolder;
  text-align: right;
  font-size: 36px;
    margin-top: 0;
  margin-bottom: 0;
}

subhead {
  font-family: roboto;
  color: black;
  font-weight: 700;
  text-align: left;
  font-size: 20px;
    padding: 0px;
}

body {
  color: black;
  font-family: roboto;
  font-weight: 400;
  font-size: 16px;
}

popuptitle {
  font-family: roboto;
  color: #00318b;
  font-weight: bolder;
  text-align: left;
  font-size: 20px;
    margin-top: 0;
  margin-bottom: 0;
}

h8 {
  color: #00318b;
  font-family: roboto;
  font-weight: 900;
  font-size: 16px;
}

table {
  font-family: roboto;
  border-collapse: collapse;
  width: 100%;
}

tr {
  border-bottom: thin solid #99a0a5;
}
  
td {
  text-align: right;
  padding: 6px;
}

th {
  text-align: right;
  padding: 6px;
}

   * {
      box-sizing: border-box;
   }
   .card {
      color: white;
      float: left;
      width: calc(25% - 20px);
      padding: 10px;
      border-radius: 10px;
      margin: 10px;
      height: 100%;
   }
   .card p {
   font-family: roboto;
   text-align: center;
   font-size: 14px;
  margin-bottom: 0;
   }
   .cardContainer:after {
      content: "";
      display: table;
      clear: both;
   }
   @media screen and (max-width: 650px) {
      .card {
         width: 100%;
      }

   }
```

```{r beats, include=FALSE}
# source("process_houston_police_beats.R")
```


```{r crimedata, include=FALSE}
# source("process_houston_crime_data.R")
```

<h2>ABC13's data team is tracking crime and safety across Houston and in your neighborhood.<br>You can choose which crime to examine: <select onchange="window.location=this.value">
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_AutoThefts.html">Auto Thefts</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Assaults.html">Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Burglaries.html">Burglaries</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_DrugCrimes.html">Drug Crimes</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker.html">Homicides</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Robberies.html">Robberies</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_SexualAssaults.html">Sexual Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Thefts.html">Thefts</option>
</select></h2>

<div class="cardContainer">
<div class="card" style="background-color:#99a0a5;">
<p>Auto Thefts<br>
<bignumber>`r prettyNum(autothefts_city$last12mos, big.mark=",")`<br></bignumber>
<p>Last 12 months<br>Through April 2022</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Auto Thefts<br>
<bignumber>`r prettyNum(round(autothefts_city$avg_prior3years,0), big.mark=",")`<br></bignumber><p>
Yearly average<br>2019 to 2021</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Auto Theft Rate<br>
<bignumber>`r round(autothefts_city$rate_last12,0)`<br></bignumber><p>
Per 100,000 people<br>Last 12 months</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Auto Theft Rate<br>
<bignumber>`r round(autothefts_city$rate_prior3years,0)`<br></bignumber><p>
Per 100,000 people<br>2019 to 2021</p>
</div>
</div>
<br>
Auto thefts are <h8>`r ifelse(autothefts_city$inc_prior3yearavgtolast12>=0," up"," down")` `r ifelse(autothefts_city$inc_prior3yearavgtolast12>=0,autothefts_city$inc_prior3yearavgtolast12,substring(autothefts_city$inc_prior3yearavgtolast12,2))`%</h8> over the last 12 months compared to the average from 2019-2021.

The city averaged <h8>`r round(autothefts_city$last12mos/52,0)`</h8> stolen vehicles a week since last May. In 2019, that number was <h8>`r round(autothefts_city$total19/52,0)`</h8> a week.

The risk is not the same neighborhood to neighborhood.

About <h8>`r round(pop_autotheftsup/2304580*100,0)`%</h8> of Houston residents live in neighborhoods where the auto theft rate is up more than 20% in the last 12 months when compared to the three-year average. About <h8>`r round(pop_autotheftsdown/2304580*100,0)`%</h8> live in neighborhoods where the auto theft rate is down or about the same. 

<subhead>Houston auto thefts neighborhood by neighborhood</subhead>

ABC13's data team looked at the Houston Police Department's data, beat by beat across the city to provide this look at trends by neighborhood from 2019 through last month.

The map color-codes each neighborhood by the motor vehicle theft rate over the last 12 months, through the end of April, which is the most recent comprehensive data released by the Houston Police Department.

The yellow areas are neighborhoods where the rate of auto thefts is among the 25% highest rates in the city. You can click on any neighborhood to see detailed figures, rates and trends.

ABC13 will be updating this data every month.
<br>
```{r cars, echo=FALSE,out.width='100%',out.height='600'}
# autotheft MAP

# Set bins for numbers of crimes for autothefts map
autotheftpal <- colorQuantile(c("#667f99",
                             "#00318b",
                             "#0058f6",
                             "#ffba00"), autothefts_beat$rate_prior3years, n = 4, na.color = NA)

# Create quick labels for autothefts map
autotheftlabel <- paste(sep="",
"<table>
<popuptitle>Houston P.D. Beat #",
autothefts_beat$beat,
"</popuptitle><br><popupchatter>Area neighborhoods and landmarks include ",
autothefts_beat$placename,
". Estimated Population: ",
prettyNum(autothefts_beat$population, big.mark=','),
"</popupchatter><br>
      <tr>
				<th></th>
				<th>Total</th>
				<th>Rate</th>
				<th>Trend</th>
			</tr>
			<tr>
				<td>2019</td>
				<td>",
autothefts_beat$total19,
"</td>
				<td>",
autothefts_beat$rate19,
"</td>
				<!-- Insert cell to cross/span 
				multi rows -->
				<td rowspan='5'>",
ifelse(autothefts_beat$inc_prior3yearavgtolast12>=0,
       "Last 12<br>months up<br><chartbignumber><span style='color:#00318b'>&#8593;</span>",
       "Last 12<br>months down <br><chartbignumber><span style='color:#00318b'>&#8595;</span>"),
ifelse(autothefts_beat$inc_prior3yearavgtolast12>=0,autothefts_beat$inc_prior3yearavgtolast12,substring(autothefts_beat$inc_prior3yearavgtolast12,2)),
				"%</chartbignumber><br>vs. 3-year<br>average</td>
			</tr>
			<tr>
				<td>2020</td>
				<td>",
autothefts_beat$total20,
"</td>
				<td>",
autothefts_beat$rate20,
"</td>
			</tr>
						<tr>
				<td>2021</td>
				<td>",
autothefts_beat$total21,
"</td>
				<td>",
autothefts_beat$rate21,
"</td>
			</tr>
						<tr>
				<td>Last 12 months</td>
				<td>",
autothefts_beat$last12mos,
"</td>
				<td>",
autothefts_beat$rate_last12,
"</td>
			</tr>
						<tr>
				<td>3-year Average</td>
				<td>",
autothefts_beat$avg_prior3years,
"</td>
				<td>",
autothefts_beat$rate_prior3years,
"</td>
			</tr>
</table>")

# Creating police beats map for types of crimes
houston_autotheft_map <- leaflet(autothefts_beat, options = leafletOptions(zoomControl = FALSE)) %>%
  htmlwidgets::onRender("function(el, x) {
L.control.zoom({ position: 'topright' }).addTo(this)
}") %>%
  setView(-95.5, 29.75, zoom = 11) %>% 
  addProviderTiles(provider = "CartoDB.Positron") %>%
  addPolygons(color = "white", 
              popup = autotheftlabel, 
              weight = 2, 
              smoothFactor = 0.5,
              opacity = 0.6, 
              fillOpacity = 0.5,
              fillColor = ~autotheftpal(rate_prior3years)) %>% 
    addSearchOSM(options = searchOptions(autoCollapse=FALSE, minLength = 3,zoom=13, position="topleft")) %>%
  addLegend(opacity = 0.6,
            values = autothefts_beat$rate_prior3years, 
            colors = c("#667f99",
                       "#00318b",
                       "#0058f6",
                       "#ffba00"),
            labels=c("Lowest Rate", 
                     "Lower Rate", 
                     "Higher Rate", 
                     "Highest Rate"),
            position = "topleft", 
            title = "<popuptitle>Houston Neighborhood Auto Thefts Map</popuptitle><br><popupchatter>Explore auto thefts per 100,000 people in your neighborhood.<br>Use the bar above to find a place, address or landmark.</popupchatter><br>") 
houston_autotheft_map
```

About <h8>`r round(pop_autotheftsmonthly/2304580*100,0)`%</h8> of Houston's reidents live in neighborhoods where there were at least 20 vehicles stolen every month over the last year. Here's a look at the figures every month since the start of 2019.

<br>
<!-- <subhead>Auto thefts month by month, 2019 through last month</subhead> -->

<iframe title="Auto thefts month by month, 2019 through last month" aria-label="Column Chart" id="datawrapper-chart-ARgCh" src="https://datawrapper.dwcdn.net/ARgCh/2/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="400" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
  <br>
<br>
<!-- <subhead>Risk of being autothefted in Houston vs. other causes of death in Texas</subhead> -->

<iframe title="Risk of property crimes across Houston" aria-label="Dot Plot" id="datawrapper-chart-HVqY5" src="https://datawrapper.dwcdn.net/HVqY5/2/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="178" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
<br>
<br>
<!-- Will be adding additional contextual charting around this crime category -->