---
title: "ABC13 Neighborhood Safety Tracker"
# author: "John Kelly"
date: "Updated 4/6/2022 by the ABC13 Data Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(tidycensus)
library(readxl)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(sp)
library(sf)
library(htmlwidgets)
library(htmltools)

# rmarkdown::render('Houston_Safety_Tracker_2.Rmd', output_file = 'docs/Houston_Safety_Tracker_2.html')
```
<link href="https://fonts.googleapis.com/css2?family=Roboto:wght@100;300;400;500;700;900&display=swap" rel="stylesheet">

```{css, echo=FALSE}

          
.title {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 45px;
    padding: 5px;
}

.date {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: center;
  font-size: 12px;
    padding: 5px;
}

select {
  margin: 0px;
  width: 175px;
  color: #00318b;
  padding: 5px 35px 5px 5px;
    font-family: roboto;
  font-size: 18px;
  font-weight: 900;
  border: 0px;
  height: 34px;
  -webkit-appearance: none;
  -moz-appearance: none;
  appearance: none;
  background: url(https://upload.wikimedia.org/wikipedia/commons/9/9d/Arrow-down.svg) 96% / 15% no-repeat #f2f2f2;
}

h1 {
  font-family: roboto;
  color: black;
  font-weight: bolder;
  text-align: left;
  font-size: 36px;
  margin-top: 0;
  margin-bottom: 0;
}

h2 {
  font-family: roboto;
  font-weight: 500;
  color: black;
  text-align: center;
  font-size: 18px;
  margin-top: 0;
  margin-bottom: 2;
}

bignumber {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 60px;
    line-height: 65px;
  height: 65px;
    margin-top: 0;
  margin-bottom: 0;
}

popupchatter {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: left;
  font-size: 13px;
  margin-top: 0;
  margin-bottom: 2;
}

chartbignumber {
  font-family: roboto;
  color: #00318b;
  font-weight: bolder;
  text-align: right;
  font-size: 36px;
    margin-top: 0;
  margin-bottom: 0;
}

subhead {
  font-family: roboto;
  color: black;
  font-weight: 700;
  text-align: left;
  font-size: 20px;
    padding: 0px;
}

body {
  color: black;
  font-family: roboto;
  font-weight: 400;
  font-size: 16px;
}

popuptitle {
  font-family: roboto;
  color: #00318b;
  font-weight: bolder;
  text-align: left;
  font-size: 20px;
    margin-top: 0;
  margin-bottom: 0;
}

h8 {
  color: #00318b;
  font-family: roboto;
  font-weight: 900;
  font-size: 16px;
}

table {
  font-family: roboto;
  border-collapse: collapse;
  width: 100%;
}

tr {
  border-bottom: thin solid #99a0a5;
}
  
td {
  text-align: right;
  padding: 6px;
}

th {
  text-align: right;
  padding: 6px;
}

   * {
      box-sizing: border-box;
   }
   .card {
      color: white;
      float: left;
      width: calc(25% - 20px);
      padding: 10px;
      border-radius: 10px;
      margin: 10px;
      height: 100%;
   }
   .card p {
   font-family: roboto;
   text-align: center;
   font-size: 14px;
  margin-bottom: 0;
   }
   .cardContainer:after {
      content: "";
      display: table;
      clear: both;
   }
   @media screen and (max-width: 650px) {
      .card {
         width: 100%;
      }

   }
```

```{r beats, include=FALSE}
# source("process_houston_police_beats.R")
```


```{r crimedata, include=FALSE}
# source("process_houston_crime_data.R")
```

<h2>ABC13's data team is tracking crime and safety across Houston and in your neighborhood.<br>You can choose which crime to examine: <select onchange="window.location=this.value">
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_SexualAssaults.html">Sexual Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Assaults.html">Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_AutoThefts.html">Auto Thefts</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Burglaries.html">Burglaries</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_DrugCrimes.html">Drug Crimes</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker.html">Homicides</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Robberies.html">Robberies</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_SexualAssaults.html">Sexual Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Thefts.html">Thefts</option>
</select></h2>

<div class="cardContainer">
<div class="card" style="background-color:#99a0a5;">
<p>Sexual Assaults<br>
<bignumber>`r prettyNum(sexassaults_city$last12mos, big.mark=",")`<br></bignumber>
<p>Last 12 months<br>Through April 2022</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Sexual Assaults<br>
<bignumber>`r prettyNum(round(sexassaults_city$avg_prior3years,0), big.mark=",")`<br></bignumber><p>
Yearly average<br>2019 to 2021</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Sexual Assault Rate<br>
<bignumber>`r sexassaults_city$rate_last12`<br></bignumber><p>
Per 100,000 people<br>Last 12 months</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Sexual Assault Rate<br>
<bignumber>`r sexassaults_city$rate_prior3years`<br></bignumber><p>
Per 100,000 people<br>2019 to 2021</p>
</div>
</div>
<br>
Sexual assaults are <h8>`r ifelse(sexassaults_city$inc_prior3yearavgtolast12>=0," up"," down")` `r ifelse(sexassaults_city$inc_prior3yearavgtolast12>=0,sexassaults_city$inc_prior3yearavgtolast12,substring(sexassaults_city$inc_prior3yearavgtolast12,2))`%</h8> over the last 12 months compared to the average from 2019-2021.

The city averaged <h8>`r round(sexassaults_city$last12mos/52,0)`</h8> sexual assaults a week since last May. In 2019, that number was <h8>`r round(sexassaults_city$total19/52,0)`</h8> a week.

The danger is not the same neighborhood to neighborhood.

About <h8>`r round(pop_sexassaultsdown/2304580*100,0)`%</h8> of Houston residents live in neighborhoods where the sexual assault rate over the last 12 months is down or about the same as the three-year average from 2019 through 2021. About <h8>`r round(pop_sexassaultsup/2304580*100,0)`%</h8> of residents live in neighborhoods where the sexual assault rate is up more than 20% over the last 12 months.

<subhead>A closer look at Houston sexual assaults neighborhood by neighborhood</subhead>

So, ABC13's data team looked at the Houston Police Department's data, beat by beat across the city to provide this look at trends by neighborhood from 2019 through last month.

The map color-codes each neighborhood by the sexual assault rate over the last 12 months, through the end of April, which is the most recent comprehensive data released by the Houston Police Department.

The yellow areas are neighborhoods where the rate is among the 25% highest rates in the city. You can click on any neighborhood to see detailed figures, rates and trends.

ABC13 will be updating this data every month.

<br>

```{r cars, echo=FALSE,out.width='100%',out.height='600'}
# sexassault MAP

# Set bins for numbers of crimes for sexassaults map
sexassaultpal <- colorQuantile(c("#667f99",
                             "#00318b",
                             "#0058f6",
                             "#ffba00"), sexassaults_beat$rate_prior3years, n = 4, na.color = NA)

# Create quick labels for sexassaults map
sexassaultlabel <- paste(sep="",
"<table>
<popuptitle>Houston P.D. Beat #",
sexassaults_beat$beat,
"</popuptitle><br><popupchatter>Area neighborhoods and landmarks include ",
sexassaults_beat$placename,
". Estimated Population: ",
prettyNum(sexassaults_beat$population, big.mark=','),
"</popupchatter><br>
      <tr>
				<th></th>
				<th>Total</th>
				<th>Rate</th>
				<th>Trend</th>
			</tr>
			<tr>
				<td>2019</td>
				<td>",
sexassaults_beat$total19,
"</td>
				<td>",
sexassaults_beat$rate19,
"</td>
				<!-- Insert cell to cross/span 
				multi rows -->
				<td rowspan='5'>",
ifelse(sexassaults_beat$inc_prior3yearavgtolast12>=0,
       "Last 12<br>months up<br><chartbignumber><span style='color:#00318b'>&#8593;</span>",
       "Last 12<br>months down <br><chartbignumber><span style='color:#00318b'>&#8595;</span>"),
ifelse(sexassaults_beat$inc_prior3yearavgtolast12>=0,sexassaults_beat$inc_prior3yearavgtolast12,substring(sexassaults_beat$inc_prior3yearavgtolast12,2)),
				"%</chartbignumber><br>vs. 3-year<br>average</td>
			</tr>
			<tr>
				<td>2020</td>
				<td>",
sexassaults_beat$total20,
"</td>
				<td>",
sexassaults_beat$rate20,
"</td>
			</tr>
						<tr>
				<td>2021</td>
				<td>",
sexassaults_beat$total21,
"</td>
				<td>",
sexassaults_beat$rate21,
"</td>
			</tr>
						<tr>
				<td>Last 12 months</td>
				<td>",
sexassaults_beat$last12mos,
"</td>
				<td>",
sexassaults_beat$rate_last12,
"</td>
			</tr>
						<tr>
				<td>3-year Average</td>
				<td>",
sexassaults_beat$avg_prior3years,
"</td>
				<td>",
sexassaults_beat$rate_prior3years,
"</td>
			</tr>
</table>")

# Creating police beats map for types of crimes
houston_sexassault_map <- leaflet(sexassaults_beat, options = leafletOptions(zoomControl = FALSE)) %>%
  htmlwidgets::onRender("function(el, x) {
L.control.zoom({ position: 'topright' }).addTo(this)
}") %>%
  setView(-95.5, 29.75, zoom = 11) %>% 
  addProviderTiles(provider = "CartoDB.Positron") %>%
  addPolygons(color = "white", 
              popup = sexassaultlabel, 
              weight = 2, 
              smoothFactor = 0.5,
              opacity = 0.6, 
              fillOpacity = 0.5,
              fillColor = ~sexassaultpal(rate_prior3years)) %>% 
    addSearchOSM(options = searchOptions(autoCollapse=FALSE, minLength = 3,zoom=13, position="topleft")) %>%
  addLegend(opacity = 0.6,
            values = sexassaults_beat$rate_prior3years, 
            colors = c("#667f99",
                       "#00318b",
                       "#0058f6",
                       "#ffba00"),
            labels=c("Lowest Rate", 
                     "Lower Rate", 
                     "Higher Rate", 
                     "Highest Rate"),
            position = "topleft", 
            title = "<popuptitle>Houston Neighborhood Sexual Assault Map</popuptitle><br><popupchatter>Explore sexual assaults per 100,000 people in your neighborhood.<br>Use the bar above to find a place, address or landmark.</popupchatter><br>") 

houston_sexassault_map
```
<br>
About <h8>`r round(pop_sexassaultsmonthly/2304580*100,0)`%</h8> of Houston residents now live in neighborhoods where there was at least one sexual assault every month over the last year. Here's a look at citywide sexual assaults every month since 2019.
<br>
<br>
<!-- <subhead>Sexual assaults month by month, 2019 through last month</subhead> -->

<iframe title="Sexual assaults month by month, 2019 through last month" aria-label="Column Chart" id="datawrapper-chart-Ao9qp" src="https://datawrapper.dwcdn.net/Ao9qp/2/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="400" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
  <br>
<br>
<!-- <subhead>Risk of sexual assault in Houston vs. other causes of death in Texas</subhead> -->

<iframe title="Risk of sexual assault in Houston vs. other severe dangers" aria-label="Dot Plot" id="datawrapper-chart-rh4Xu" src="https://datawrapper.dwcdn.net/rh4Xu/2/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="151" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
<br>
<br>
<!-- Will be adding additional contextual charting around this crime category -->