---
title: __`r subgroup$agency_short` police accountability watch__
author: "This report brings together in one place all of the publicly-available data about the __`r subgroup$agency_short`__ police department, located in `r subgroup$county`, Calif., including data about the agency's size, spending, performance solving crimes, use of force and citizen complaints, as gathered from public records by ABC Owned Television Stations."
output: html_document
---
UPDATED JUNE 25, 2020

```{css, echo=FALSE}
h1 {
  color: black;
  font-family: Roboto;
}
h2 {
  color: #001f4c;
  font-family: arial;
}
h3 {
  color: #C8490F;
  font-family: arial;
}
body {
  color: black;
  font-family: times, serif;
}
h5 {
  color: white;
  background-color: #5397ff;
  font-family: arial;
  border-radius: 10px;
  padding: 1em;
  text-align: center;
}
```
<br>

##### This agency solved __`r subgroup$violent_pct`%__ of its violent crimes.

##### This agency solved __`r subgroup$property_pct`%__ of its property crimes.

##### This agency spent __$`r subgroup$spendper1K`__ per 1,000 residents.

##### This agency has __`r subgroup$policeper1K`__ officers per 1,000 residents.

##### This agency arrests black people at __`r subgroup$times_more_likely`__ times the rate of white people.

##### This agency reported __1,000,000__ use of force incidents.

##### This agency received __1,000,000__ citizen complaints.

## __Size and spending__



## __Violent crimes__

The agency reported 

### __`r prettyNum(subgroup$violent_sum, big.mark=",")`__

violent crimes in 2018, clearing `r prettyNum(subgroup$violent_clr_sum, big.mark=",")` of those by arrest.

That's a clearance rate of about 

### __`r subgroup$violent_pct`%__

compared to `r meanviol`% for all departments in California.

Here's a look at the clearance rate historically for violent crimes by `r subgroup$agency_short` police.

```{r, echo=FALSE, out.width='100%'}
library(plotly)
agencyclearance <- filter(clearance, ncic_code == agency)
fig <- plot_ly(agencyclearance, x = ~year, y = ~violent_sum, type = 'bar', name = 'Violent crimes', marker=list(color = "#154FC2"))
fig <- fig %>% add_trace(y = ~violent_clr_sum, name = 'Cleared', marker=list(color = "#C8490F"))
fig <- fig %>% layout(yaxis = list(title = 'Count'), barmode = 'group')

fig
```

## __Property crimes__

The agency reported 

### __`r prettyNum(subgroup$property_sum, big.mark=",")`__

property crimes in 2018, clearing `r prettyNum(subgroup$property_clr_sum,  big.mark=",")` of those by arrest.

That's a clearance rate of about 

### __`r subgroup$property_pct`%__

compared to the average of `r meanprop`% for property crimes across all departments in California.

```{r, echo=FALSE, out.width='100%'}
agencyclearance <- filter(clearance, ncic_code == agency)
library(plotly)
fig2 <- plot_ly(agencyclearance, x = ~year, y = ~property_sum, type = 'bar', name = 'Property crimes', marker=list(color = "#154FC2"))
fig2 <- fig2 %>% add_trace(y = ~property_clr_sum, name = 'Cleared', marker=list(color = "#C8490F"))
fig2 <- fig2 %>% layout(yaxis = list(title = 'Count'), barmode = 'group')

fig2
```

