---
title: "ABC13 Neighborhood Safety Tracker"
# author: "John Kelly"
date: "Updated `r format(Sys.time(), '%B %d, %Y')` by the ABC13 Data Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(tidycensus)
library(readxl)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(sp)
library(sf)
library(htmlwidgets)
library(htmltools)

# rmarkdown::render('Houston_Safety_Tracker_2.Rmd', output_file = 'docs/Houston_Safety_Tracker_2.html')
```
<link href="https://fonts.googleapis.com/css2?family=Roboto:wght@100;300;400;500;700;900&display=swap" rel="stylesheet">

```{css, echo=FALSE}

          
.title {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 45px;
    padding: 5px;
}

.date {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: center;
  font-size: 12px;
    padding: 5px;
}

select {
  margin: 0px;
  width: 180px;
  color: #00318b;
  padding: 5px 35px 5px 5px;
    font-family: roboto;
  font-size: 18px;
  font-weight: 900;
  border: 0px;
  height: 34px;
  -webkit-appearance: none;
  -moz-appearance: none;
  appearance: none;
  background: url(https://upload.wikimedia.org/wikipedia/commons/9/9d/Arrow-down.svg) 96% / 15% no-repeat #f2f2f2;
}

h1 {
  font-family: roboto;
  color: black;
  font-weight: bolder;
  text-align: left;
  font-size: 36px;
  margin-top: 0;
  margin-bottom: 0;
}

h2 {
  font-family: roboto;
  font-weight: 500;
  color: black;
  text-align: center;
  font-size: 18px;
  margin-top: 0;
  margin-bottom: 2;
}

bignumber {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 60px;
    line-height: 65px;
  height: 65px;
    margin-top: 0;
  margin-bottom: 0;
}

subhead {
  font-family: roboto;
  color: black;
  font-weight: 700;
  text-align: left;
  font-size: 20px;
    padding: 0px;
}

body {
  color: black;
  font-family: roboto;
  font-weight: 400;
  font-size: 18px;
}

popuptitle {
  color: #00318b;
  font-family: roboto;
  font-weight: 700;
  font-size: 15px;
  text-align: left;
}

popupchatter {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: left;
  font-size: 12px;
  margin-top: 0;
  margin-bottom: 2;
}

h8 {
  color: #00318b;
  font-family: roboto;
  font-weight: 900;
  font-size: 18px;
}

table {
  font-family: roboto;
  width: 100%;
}

tr {
  border-bottom: thin solid #99a0a5;
}
  
td {
  text-align: right;
  padding: 1px;
}

th {
  text-align: right;
  padding: 1px;
}

   * {
      box-sizing: border-box;
   }
   .card {
      color: white;
      float: left;
      width: calc(25% - 20px);
      padding: 10px;
      border-radius: 10px;
      margin: 10px;
      height: 100%;
   }
   .card p {
   font-family: roboto;
   text-align: center;
   font-size: 14px;
  margin-bottom: 0;
   }
   .cardContainer:after {
      content: "";
      display: table;
      clear: both;
   }
   @media screen and (max-width: 650px) {
      .card {
         width: 100%;
      }

   }
```

```{r beats, include=FALSE}
# source("process_houston_police_beats.R")
```


```{r crimedata, include=FALSE}
# source("process_houston_crime_data.R")
```

<h2>ABC13 is tracking crime and safety across Houston and in your neighborhood.<br>You can choose which crime to examine: <select onchange="window.location=this.value">
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Robberies.html">Robberies</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Assaults.html">Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_AutoThefts.html">Auto Thefts</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Burglaries.html">Burglaries</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_DrugCrimes.html">Drug Crimes</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker.html">Homicides</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Robberies.html">Robberies</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_SexualAssaults.html">Sexual Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Thefts.html">Thefts</option>
</select></h2>

<div class="cardContainer">
<div class="card" style="background-color:#99a0a5;">
<p>Robberies<br>
<bignumber>`r prettyNum(robberies_city$last12mos, big.mark=",")`<br></bignumber>
<p>Last 12 months<br>Through June 2022</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Robberies<br>
<bignumber>`r prettyNum(round(robberies_city$avg_prior3years,0), big.mark=",")`<br></bignumber><p>
Yearly average<br>2019 to 2021</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Robbery Rate<br>
<bignumber>`r round(robberies_city$rate_last12,0)`<br></bignumber><p>
Per 100,000 people<br>Last 12 months</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Robbery Rate<br>
<bignumber>`r round(robberies_city$rate_prior3years,0)`<br></bignumber><p>
Per 100,000 people<br>2019 to 2021</p>
</div>
</div>
<br>
Robberies are <h8>`r ifelse(robberies_city$inc_prior3yearavgtolast12>=0," up"," down")` `r ifelse(robberies_city$inc_prior3yearavgtolast12>=0,robberies_city$inc_prior3yearavgtolast12,substring(robberies_city$inc_prior3yearavgtolast12,2))`%</h8> over the last 12 months compared to the average from 2019-2021.

The city averaged <h8>`r round(robberies_city$last12mos/52,0)`</h8> robberies a week since last June. In 2019, that number was <h8>`r round(robberies_city$total19/52,0)`</h8> a week.

The risk is not the same neighborhood to neighborhood.

About <h8>`r round(pop_robberiesdown/2304580*100,0)`%</h8> of city residents live in neighborhoods where the robbery rate over the last 12 months is down or about the same as the three-year average. About <h8>`r round(pop_robberiesup/2304580*100,0)`%</h8> live in neighborhoods where the robbery rate is up more than 20%.

ABC13's data team looked at the Houston Police Department's data by neighborhood from 2019 through last month.

<subhead>A closer look at Houston robberies neighborhood by neighborhood</subhead>

The map color-codes each neighborhood by the robbery rate over the last 12 months, through the end of June, which is the most recent comprehensive data released by the Houston Police Department.

The yellow areas are neighborhoods where the robbery rate is among the 25% highest rates in the city.

Click on any neighborhood on the map to see detailed figures, rates and trends. You can also search for a street name, place, landmark or zip code.

<br>
```{r cars, echo=FALSE,out.width='100%',out.height='600'}
# robbery MAP

# Set bins for numbers of crimes for robberies map
robberypal <- colorQuantile(c("#667f99",
                             "#00318b",
                             "#0058f6",
                             "#ffba00",
                       "#be0000"), robberies_beat$rate_last12, n = 5, na.color = NA)

# Create quick labels for robberies map
robberylabel <- paste(sep="",
ifelse(robberies_beat$inc_prior3yearavgtolast12>=0,
       "<popuptitle>Robberies are up ",
       "<popuptitle>Robberies are down "),
ifelse(robberies_beat$inc_prior3yearavgtolast12>=0,robberies_beat$inc_prior3yearavgtolast12,substring(robberies_beat$inc_prior3yearavgtolast12,2)),
				"%</popuptitle><br><popupchatter>the last 12 months vs. the 3-year average in the area including ",
robberies_beat$placename,
", home to an estimated ",
prettyNum(robberies_beat$population, big.mark=","),
" people.
<br>
<table>      
      <tr>
				<th></th>
				<th>Total</th>
				<th>Rate</th>
			</tr>
			<tr>
				<td>2019</td>
				<td>",
robberies_beat$total19,
"</td>
				<td>",
round(robberies_beat$rate19,0),
"</td>
			</tr>
			<tr>
				<td>2020</td>
				<td>",
robberies_beat$total20,
"</td>
				<td>",
round(robberies_beat$rate20,0),
"</td>
			</tr>
						<tr>
				<td>2021</td>
				<td>",
robberies_beat$total21,
"</td>
				<td>",
round(robberies_beat$rate21,0),
"</td>
			</tr>
						<tr>
				<td>Last 12 months</td>
				<td>",
robberies_beat$last12mos,
"</td>
				<td>",
round(robberies_beat$rate_last12,0),
"</td>
			</tr>
						<tr>
				<td>3-year Average</td>
				<td>",
round(robberies_beat$avg_prior3years,0),
"</td>
				<td>",
round(robberies_beat$rate_prior3years,0),
"</td>
			</tr>
</table>")

# Creating police beats map for types of crimes
houston_robbery_map <- leaflet(robberies_beat, options = leafletOptions(zoomControl = FALSE, zoomSnap = 0.5, zoomDelta=0.5)) %>%
  htmlwidgets::onRender("function(el, x) {
L.control.zoom({ position: 'topright' }).addTo(this)
}") %>%
  setView(-95.45, 29.75, zoom = 10.5) %>% 
  addProviderTiles(provider = "CartoDB.Positron") %>%
  addPolygons(color = "white", 
              popup = robberylabel, 
              popupOptions = popupOptions(maxWidth ="200", 
                                          minWidth ="200"),
              weight = 2, 
              smoothFactor = 0.5,
              opacity = 0.6, 
              fillOpacity = 0.5,
              fillColor = ~robberypal(rate_prior3years)) %>% 
    addSearchOSM(options = searchOptions(autoCollapse=FALSE, minLength = 3,zoom=13, position="topleft")) %>%
    onRender("function(el, x) {
        $('input.search-input')[0].placeholder = 'Search street, place or zip code'
        }") %>%
  addLegend(opacity = 0.6,
            values = robberies_beat$rate_last12, 
            colors = c("#667f99",
                       "#00318b",
                       "#0058f6",
                       "#ffba00",
                       "#be0000"),
            labels=c("Lowest Rate", 
                     "Lower Rate", 
                     "High Rate", 
                     "Higher Rate",
                     "Highest Rate"),
            position = "bottomleft", 
            title = "<popuptitle>Robberies per 100,000 people")  

houston_robbery_map
```

<br>
About <h8>`r round(pop_burglariesmonthly/2304580*100,0)`%</h8> of Houston residents now live in neighborhoods where there was at least one robbery every month over the last year. Here's a look at robberies citywide every month since 2019.
<br>
<br>
<!-- <subhead>Robberies month by month, 2019 through last month</subhead> -->

<iframe title="Robberies month by month, 2019 through last month" aria-label="Column Chart" id="datawrapper-chart-6BRuf" src="https://datawrapper.dwcdn.net/6BRuf/2/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="400" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
  <br>
<br>
<!-- <subhead>Risk of assault and other crimes in Houston </subhead> -->

<iframe title="Risk of violent crimes compared to other kinds of deaths, injuries" aria-label="Dot Plot" id="datawrapper-chart-rh4Xu" src="https://datawrapper.dwcdn.net/rh4Xu/7/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="214" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
<br>