---
title: "ABC13 Neighborhood Safety Tracker"
# author: "John Kelly"
date: "Updated `r format(Sys.time(), '%B %d, %Y')` by the ABC13 Data Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(tidycensus)
library(readxl)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(sp)
library(sf)
library(htmlwidgets)
library(htmltools)

# rmarkdown::render('Houston_Safety_Tracker_2.Rmd', output_file = 'docs/Houston_Safety_Tracker_2.html')
```
<link href="https://fonts.googleapis.com/css2?family=Roboto:wght@100;300;400;500;700;900&display=swap" rel="stylesheet">

```{css, echo=FALSE}

          
.title {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 45px;
    padding: 5px;
}

.date {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: center;
  font-size: 12px;
    padding: 5px;
}

select {
  margin: 0px;
  width: 180px;
  color: #00318b;
  padding: 5px 35px 5px 5px;
    font-family: roboto;
  font-size: 18px;
  font-weight: 900;
  border: 0px;
  height: 34px;
  -webkit-appearance: none;
  -moz-appearance: none;
  appearance: none;
  background: url(https://upload.wikimedia.org/wikipedia/commons/9/9d/Arrow-down.svg) 96% / 15% no-repeat #f2f2f2;
}

h1 {
  font-family: roboto;
  color: black;
  font-weight: bolder;
  text-align: left;
  font-size: 36px;
  margin-top: 0;
  margin-bottom: 0;
}

h2 {
  font-family: roboto;
  font-weight: 500;
  color: black;
  text-align: center;
  font-size: 18px;
  margin-top: 0;
  margin-bottom: 2;
}

bignumber {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 60px;
    line-height: 65px;
  height: 65px;
    margin-top: 0;
  margin-bottom: 0;
}

subhead {
  font-family: roboto;
  color: black;
  font-weight: 700;
  text-align: left;
  font-size: 20px;
    padding: 0px;
}

body {
  color: black;
  font-family: roboto;
  font-weight: 400;
  font-size: 18px;
}

popuptitle {
  color: #00318b;
  font-family: roboto;
  font-weight: 700;
  font-size: 15px;
  text-align: left;
}

popupchatter {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: left;
  font-size: 12px;
  margin-top: 0;
  margin-bottom: 2;
}

h8 {
  color: #00318b;
  font-family: roboto;
  font-weight: 900;
  font-size: 18px;
}

table {
  font-family: roboto;
  width: 100%;
}

tr {
  border-bottom: thin solid #99a0a5;
}
  
td {
  text-align: right;
  padding: 1px;
}

th {
  text-align: right;
  padding: 1px;
}

   * {
      box-sizing: border-box;
   }
   .card {
      color: white;
      float: left;
      width: calc(25% - 20px);
      padding: 10px;
      border-radius: 10px;
      margin: 10px;
      height: 100%;
   }
   .card p {
   font-family: roboto;
   text-align: center;
   font-size: 14px;
  margin-bottom: 0;
   }
   .cardContainer:after {
      content: "";
      display: table;
      clear: both;
   }
   @media screen and (max-width: 650px) {
      .card {
         width: 100%;
      }

   }
```

```{r beats, include=FALSE}
# source("process_houston_police_beats.R")
```


```{r crimedata, include=FALSE}
# source("process_houston_crime_data.R")
```

<h2>ABC13's data team is tracking crime and safety across Houston and in your neighborhood.<br>You can choose which crime to examine: <select onchange="window.location=this.value">
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Burglaries.html">Burglaries</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Assaults.html">Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_AutoThefts.html">Auto Thefts</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Burglaries.html">Burglaries</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_DrugCrimes.html">Drug Crimes</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker.html">Homicides</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Robberies.html">Robberies</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_SexualAssaults.html">Sexual Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Thefts.html">Thefts</option>
</select></h2>

<div class="cardContainer">
<div class="card" style="background-color:#99a0a5;">
<p>Burglaries<br>
<bignumber>`r prettyNum(burglaries_city$last12mos, big.mark=",")`<br></bignumber>
<p>Last 12 months<br>Through July 2022</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Burglaries<br>
<bignumber>`r prettyNum(round(burglaries_city$avg_prior3years,0), big.mark=",")`<br></bignumber><p>
Yearly average<br>2019 to 2021</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Burglary Rate<br>
<bignumber>`r round(burglaries_city$rate_last12,0)`<br></bignumber><p>
Per 100,000 people<br>Last 12 months</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Burglary Rate<br>
<bignumber>`r round(burglaries_city$rate_prior3years,0)`<br></bignumber><p>
Per 100,000 people<br>2019 to 2021</p>
</div>
</div>
<br>
Burglaries are <h8>`r ifelse(burglaries_city$inc_prior3yearavgtolast12>=0," up"," down")` `r ifelse(burglaries_city$inc_prior3yearavgtolast12>=0,burglaries_city$inc_prior3yearavgtolast12,substring(burglaries_city$inc_prior3yearavgtolast12,2))`%</h8> over the last 12 months compared to the average from 2019-2021.

The city averaged <h8>`r round(burglaries_city$last12mos/52,0)`</h8> burglaries a week since last July. In 2019, that number was <h8>`r round(burglaries_city$total19/52,0)`</h8> a week.

<subhead>A closer look at Houston burglaries neighborhood by neighborhood</subhead>

The risk is not the same neighborhood to neighborhood. ABC13's data team looked at the Houston Police Department's data by neighborhood from 2019 through last month.

The map color-codes each neighborhood by the burglary rate over the last 12 months. The three darker blues represent neighborhoods with burglary rates that are higher than the citywide rate. You can also click the box in the bottom right corner to see neighborhoods by the number of burglaries.

Click on any neighborhood on the map to see detailed numbers, rates and trends. You can also search for a street name, place, landmark or zip code.

<br>
```{r cars, echo=FALSE,out.width='100%',out.height='600'}
# burglary MAP

# Set bins for numbers of crimes for burglaries map
burglarybins1 <- c(0,
                300,
                600,
                800,
                1000,
                1500)
burglarybins2 <- c(0,
                   50,
                100,
                200,
                300,
                400)
burglarypal1 <- colorBin(c("#99a0a5",
                             "#2787d6",
                             "#0058f6",
                             "#003ca6",
                             "#00215c"), burglaries_beat$rate_last12, bins = burglarybins1,na.color = "#51585f")

burglarypal2 <- colorBin(c("#99a0a5",
                             "#2787d6",
                             "#0058f6",
                             "#003ca6",
                             "#00215c"), burglaries_beat$last12mos, bins = burglarybins2,na.color = "#51585f")


# Create quick labels for burglaries map
burglarylabel <- paste(sep="",
ifelse(burglaries_beat$inc_prior3yearavgtolast12>=0,
       "<popuptitle>Burglaries are up ",
       "<popuptitle>Burglaries are down "),
ifelse(burglaries_beat$inc_prior3yearavgtolast12>=0,burglaries_beat$inc_prior3yearavgtolast12,substring(burglaries_beat$inc_prior3yearavgtolast12,2)),
				"%</popuptitle><br><popupchatter>the last 12 months vs. the 3-year average in the area including ",
burglaries_beat$placename,
", home to an estimated ",
prettyNum(burglaries_beat$population, big.mark=","),
" people.
<br>
<table>      
      <tr>
				<th></th>
				<th>Total</th>
				<th>Rate</th>
			</tr>
			<tr>
				<td>2019</td>
				<td>",
burglaries_beat$total19,
"</td>
				<td>",
round(burglaries_beat$rate19,0),
"</td>
			</tr>
			<tr>
				<td>2020</td>
				<td>",
burglaries_beat$total20,
"</td>
				<td>",
round(burglaries_beat$rate20,0),
"</td>
			</tr>
						<tr>
				<td>2021</td>
				<td>",
burglaries_beat$total21,
"</td>
				<td>",
round(burglaries_beat$rate21,0),
"</td>
			</tr>
						<tr>
				<td>Last 12 months</td>
				<td>",
burglaries_beat$last12mos,
"</td>
				<td>",
round(burglaries_beat$rate_last12,0),
"</td>
			</tr>
						<tr>
				<td>3-year Average</td>
				<td>",
round(burglaries_beat$avg_prior3years,0),
"</td>
				<td>",
round(burglaries_beat$rate_prior3years,0),
"</td>
			</tr>
</table>")

# Creating police beats map for types of crimes
houston_burglary_map <- leaflet(burglaries_beat, options = leafletOptions(zoomControl = FALSE, zoomSnap = 0.5, zoomDelta=0.5)) %>%
  htmlwidgets::onRender("function(el, x) {
L.control.zoom({ position: 'topright' }).addTo(this)
}") %>%
  setView(-95.45, 29.75, zoom = 10.5) %>% 
  addProviderTiles(provider = "CartoDB.Positron") %>%
  addPolygons(color = "white", 
              popup = burglarylabel,
              popupOptions = popupOptions(maxWidth ="200", 
                                          minWidth ="200"),
              weight = 2, 
              smoothFactor = 0.5,
              opacity = 0.6, 
              fillOpacity = 0.6,
              fillColor = ~burglarypal1(rate_last12),
              group="Rate") %>% 
    addPolygons(color = "white", 
              popup = burglarylabel,
              popupOptions = popupOptions(maxWidth ="200", 
                                          minWidth ="200"),
              weight = 2, 
              smoothFactor = 0.5,
              opacity = 0.6, 
              fillOpacity = 0.6,
              fillColor = ~burglarypal2(last12mos),
              group="Number") %>% 
    addSearchOSM(options = searchOptions(autoCollapse=FALSE, minLength = 3,zoom=13, position="topleft")) %>%
    onRender("function(el, x) {
        $('input.search-input')[0].placeholder = 'Search street, place or zip code'
        }") %>%
  addLegend(opacity = 0.6,
            values = burglaries_beat$rate_last12, 
            pal = burglarypal1,
            position = "bottomleft", 
            title = paste(sep="","<popuptitle>Burglary Rate<br><popupchatter>Burglaries/100K people<br>Citywide: ",prettyNum(round(burglaries_city$rate_last12,0), big.mark=",")),
            group = "Rate",
            className = "info legend Rate") %>%
  addLegend(opacity = 0.6,
            values = burglaries_beat$last12mos, 
            pal = burglarypal2,
            position = "bottomleft", 
            title = paste(sep="","<popuptitle>Burglaries<br><popupchatter>Total burglaries<br>Citywide: ",prettyNum(round(burglaries_city$last12mos,0), big.mark=",")),
            group = "Number",
            className = "info legend Number") %>%
  addLayersControl(
    baseGroups = c("Rate","Number"),
    options = layersControlOptions(collapsed = FALSE),
    position = 'bottomright') %>% hideGroup(c("Number")) %>%
   htmlwidgets::onRender("
      function(el, x) {
         var updateLegend = function () {
            var selectedGroup = document.querySelectorAll('input:checked')[0].nextSibling.innerText.substr(1);

            document.querySelectorAll('.legend').forEach(a => a.hidden=true);
            document.querySelectorAll('.legend').forEach(l => {
               if (l.classList.contains(selectedGroup)) l.hidden=false;
            });
         };
         updateLegend();
         this.on('baselayerchange', el => updateLegend());
      }"
   )
houston_burglary_map
```
<br>
<br>
<!-- <subhead>Burglaries month by month, 2019 through last month</subhead> -->

<iframe title="Burglaries month by month, 2019 through last month" aria-label="Column Chart" id="datawrapper-chart-gG4we" src="https://datawrapper.dwcdn.net/gG4we/1/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="400" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
  <br>
<br>
<!-- <subhead>Risk of being burglarized in Houston vs. other crimes in Houston</subhead> -->

<iframe title="Risk of property crimes across Houston" aria-label="Dot Plot" id="datawrapper-chart-HVqY5" src="https://datawrapper.dwcdn.net/HVqY5/5/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="178" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
<br>
<br>
<!-- Will be adding additional contextual charting around this crime category -->