---
title: "ABC13 Neighborhood Safety Tracker"
# author: "John Kelly"
date: "Updated `r format(Sys.time(), '%B %d, %Y')` by the ABC13 Data Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(tidycensus)
library(readxl)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(sp)
library(sf)
library(htmlwidgets)
library(htmltools)

# rmarkdown::render('Houston_Safety_Tracker_2.Rmd', output_file = 'docs/Houston_Safety_Tracker_2.html')
```
<link href="https://fonts.googleapis.com/css2?family=Roboto:wght@100;300;400;500;700;900&display=swap" rel="stylesheet">

```{css, echo=FALSE}

          
.title {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 45px;
    padding: 5px;
}

.date {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: center;
  font-size: 12px;
    padding: 5px;
}

select {
  margin: 0px;
  width: 180px;
  color: #00318b;
  padding: 5px 35px 5px 5px;
    font-family: roboto;
  font-size: 18px;
  font-weight: 900;
  border: 0px;
  height: 34px;
  -webkit-appearance: none;
  -moz-appearance: none;
  appearance: none;
  background: url(https://upload.wikimedia.org/wikipedia/commons/9/9d/Arrow-down.svg) 96% / 15% no-repeat #f2f2f2;
}

h1 {
  font-family: roboto;
  color: black;
  font-weight: bolder;
  text-align: left;
  font-size: 36px;
  margin-top: 0;
  margin-bottom: 0;
}

h2 {
  font-family: roboto;
  font-weight: 500;
  color: black;
  text-align: center;
  font-size: 18px;
  margin-top: 0;
  margin-bottom: 2;
}

bignumber {
  font-family: roboto;
  color: #00318b;
  font-weight: 900;
  text-align: center;
  font-size: 60px;
    line-height: 65px;
  height: 65px;
    margin-top: 0;
  margin-bottom: 0;
}

subhead {
  font-family: roboto;
  color: black;
  font-weight: 700;
  text-align: left;
  font-size: 20px;
    padding: 0px;
}

body {
  color: black;
  font-family: roboto;
  font-weight: 400;
  font-size: 18px;
}

popuptitle {
  color: #00318b;
  font-family: roboto;
  font-weight: 700;
  font-size: 15px;
  text-align: left;
}

popupchatter {
  font-family: roboto;
  color: black;
  font-weight: 300;
  text-align: left;
  font-size: 12px;
  margin-top: 0;
  margin-bottom: 2;
}

h8 {
  color: #00318b;
  font-family: roboto;
  font-weight: 900;
  font-size: 18px;
}

table {
  font-family: roboto;
  width: 100%;
}

tr {
  border-bottom: thin solid #99a0a5;
}
  
td {
  text-align: right;
  padding: 1px;
}

th {
  text-align: right;
  padding: 1px;
}

   * {
      box-sizing: border-box;
   }
   .card {
      color: white;
      float: left;
      width: calc(25% - 20px);
      padding: 10px;
      border-radius: 10px;
      margin: 10px;
      height: 100%;
   }
   .card p {
   font-family: roboto;
   text-align: center;
   font-size: 14px;
  margin-bottom: 0;
   }
   .cardContainer:after {
      content: "";
      display: table;
      clear: both;
   }
   @media screen and (max-width: 650px) {
      .card {
         width: 100%;
      }

   }
```

```{r beats, include=FALSE}
# source("process_houston_police_beats.R")
```


```{r crimedata, include=FALSE}
# source("process_houston_crime_data.R")
```

<h2>ABC13's data team is tracking crime and safety across Houston and in your neighborhood.<br>You can choose which crime to examine: <select onchange="window.location=this.value">
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Assaults.html">Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Assaults.html">Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_AutoThefts.html">Auto Thefts</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Burglaries.html">Burglaries</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_DrugCrimes.html">Drug Crimes</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker.html">Homicides</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Robberies.html">Robberies</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_SexualAssaults.html">Sexual Assaults</option>
<option value="https://abcotvdata.github.io/safetytracker_houston/Houston_Safety_Tracker_Thefts.html">Thefts</option>
</select></h2>

<div class="cardContainer">
<div class="card" style="background-color:#99a0a5;">
<p>Assaults<br>
<bignumber>`r prettyNum(assaults_city$last12mos, big.mark=",")`<br></bignumber>
<p>Last 12 months<br>Through April 2022</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Assaults<br>
<bignumber>`r prettyNum(round(assaults_city$avg_prior3years,0), big.mark=",")`<br></bignumber><p>
Yearly average<br>2019 to 2021</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Assault Rate<br>
<bignumber>`r prettyNum(round(assaults_city$rate_last12,0), big.mark=",")`<br></bignumber><p>
Per 100,000 people<br>Last 12 months</p>
</div>
<div class="card" style="background-color:#99a0a5;">
<p>Average Assault Rate<br>
<bignumber>`r prettyNum(round(assaults_city$rate_prior3years,0), big.mark=",")`<br></bignumber><p>
Per 100,000 people<br>2019 to 2021</p>
</div>
</div>
<br>
Assaults are <h8>`r ifelse(assaults_city$inc_prior3yearavgtolast12>=0," up"," down")` `r ifelse(assaults_city$inc_prior3yearavgtolast12>=0,assaults_city$inc_prior3yearavgtolast12,substring(assaults_city$inc_prior3yearavgtolast12,2))`%</h8> over the last 12 months compared to the average from 2019-2021.

The city averaged <h8>`r prettyNum(round(assaults_city$last12mos/52,0), big.mark=",")`</h8> assaults a week since last May. In 2019, that number was <h8>`r prettyNum(round(assaults_city$total19/52,0), big.mark=",")`</h8> a week.

The danger is not the same neighborhood to neighborhood.

About <h8>`r round(pop_assaultsdown/2304580*100,0)`%</h8> of Houston residents live in neighborhoods where the assault rate over the last 12 months is down or about the same as the three-year average from 2019 through 2021. About <h8>`r round(pop_assaultsup/2304580*100,0)`%</h8> of residents live in neighborhoods where the assault rate is up more than 20% over the last 12 months.

ABC13's data team looked at the Houston Police Department's data by neighborhood from 2019 through last month.

<subhead>A closer look at Houston assaults neighborhood by neighborhood</subhead>

The map color-codes each neighborhood by the assault rate over the last 12 months, through the end of April, which is the most recent comprehensive data released by the Houston Police Department.

The yellow areas are neighborhoods where the rate is among the 25% highest rates in the city.

Click on any neighborhood on the map to see detailed figures, rates and trends. You can also search for a street name, place, landmark or zip code.

<br>

```{r cars, echo=FALSE,out.width='100%',out.height='600'}
# assault MAP

# Set bins for numbers of crimes for assaults map
assaultpal <- colorQuantile(c("#667f99",
                             "#00318b",
                             "#0058f6",
                             "#ffba00"), assaults_beat$rate_prior3years, n = 4, na.color = NA)

# Create quick labels for assaults map
assaultlabel <- paste(sep="",
ifelse(assaults_beat$inc_prior3yearavgtolast12>=0,
       "<popuptitle>Assaults are up ",
       "<popuptitle>Assaults are down "),
ifelse(assaults_beat$inc_prior3yearavgtolast12>=0,assaults_beat$inc_prior3yearavgtolast12,substring(assaults_beat$inc_prior3yearavgtolast12,2)),
				"%</popuptitle><br><popupchatter>the last 12 months vs. the 3-year average in the area including ",
assaults_beat$placename,
".
<br>
<table>      
      <tr>
				<th></th>
				<th>Total</th>
				<th>Rate</th>
			</tr>
			<tr>
				<td>2019</td>
				<td>",
assaults_beat$total19,
"</td>
				<td>",
prettyNum(round(assaults_beat$rate19,0), big.mark=","),
"</td>
			</tr>
			<tr>
				<td>2020</td>
				<td>",
assaults_beat$total20,
"</td>
				<td>",
prettyNum(round(assaults_beat$rate20,0), big.mark=","),
"</td>
			</tr>
						<tr>
				<td>2021</td>
				<td>",
assaults_beat$total21,
"</td>
				<td>",
prettyNum(round(assaults_beat$rate21,0), big.mark=","),
"</td>
			</tr>
						<tr>
				<td>Last 12 months</td>
				<td>",
assaults_beat$last12mos,
"</td>
				<td>",
prettyNum(round(assaults_beat$rate_last12,0), big.mark=","),
"</td>
			</tr>
						<tr>
				<td>3-year Average</td>
				<td>",
round(assaults_beat$avg_prior3years,0),
"</td>
				<td>",
prettyNum(round(assaults_beat$rate_prior3years,0), big.mark=","),
"</td>
			</tr>
</table>")

# Creating police beats map for types of crimes
houston_assault_map <- leaflet(assaults_beat, options = leafletOptions(zoomControl = FALSE, zoomSnap = 0.5, zoomDelta=0.5)) %>%
  htmlwidgets::onRender("function(el, x) {
L.control.zoom({ position: 'topright' }).addTo(this)
}") %>%
  setView(-95.45, 29.75, zoom = 10.5) %>% 
  addProviderTiles(provider = "CartoDB.Positron") %>%
  addPolygons(color = "white", 
              popup = assaultlabel, 
              popupOptions = popupOptions(maxWidth ="200", 
                                          minWidth ="200"),
              weight = 2, 
              smoothFactor = 0.5,
              opacity = 0.6, 
              fillOpacity = 0.5,
              fillColor = ~assaultpal(rate_prior3years)) %>% 
  addSearchOSM(options = searchOptions(autoCollapse=FALSE, minLength = 3,zoom=13, position="topleft")) %>%
  addLegend(opacity = 0.6,
            values = assaults_beat$rate_prior3years, 
            colors = c("#667f99",
                       "#00318b",
                       "#0058f6",
                       "#ffba00"),
            labels=c("Lowest Rate", 
                     "Lower Rate", 
                     "Higher Rate", 
                     "Highest Rate"),
            position = "bottomleft", 
            title = "<popuptitle>Assaults per 100,000 people")  
houston_assault_map
```
<br>
About <h8>`r round(pop_assaultsmonthly/2304580*100,0)`%</h8> of Houston residents now live in neighborhoods where there was at least one assault every month over the last year. Here's a look at citywide assaults every month since 2019.
<br>
<br>
<!-- <subhead>Assaults month by month, 2019 through last month</subhead> -->

<iframe title="Assaults month by month, 2019 through last month" aria-label="Column Chart" id="datawrapper-chart-DQ70W" src="https://datawrapper.dwcdn.net/DQ70W/2/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="400" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
  <br>
<br>
<!-- <subhead>Risk of assault and other violent crimes in Houston </subhead> -->

<iframe title="Risk of violent crimes compared to other kinds of deaths, injuries" aria-label="Dot Plot" id="datawrapper-chart-rh4Xu" src="https://datawrapper.dwcdn.net/rh4Xu/7/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height="214" data-external="1"></iframe><script type="text/javascript">!function(){"use strict";window.addEventListener("message",(function(e){if(void 0!==e.data["datawrapper-height"]){var t=document.querySelectorAll("iframe");for(var a in e.data["datawrapper-height"])for(var r=0;r<t.length;r++){if(t[r].contentWindow===e.source)t[r].style.height=e.data["datawrapper-height"][a]+"px"}}}))}();
</script>
<br>
<br>
